|

### 2023-06-09 full-paper/paper.Rmd
paper: use hi-res figures and set width as text width

```{r}
#| ssp,
#| echo = FALSE,
#| eval = TRUE,
#| fig.cap = "Scenario design matrix for future climate prediction based on SSP
#|   and RCP in ScenarioMIP\\citep{oneill2016scenario}"

knitr::include_graphics("figures/ssp.png")
```

@@

```{r}
#| workflow,
#| echo = FALSE,
#| eval = TRUE,
#| fig.cap = "The primary process of using epwshiftr to generate EPW files for future weather"

knitr::include_graphics("figures/workflow.png")
```

>>>>

```{r}
#| ssp,
#| echo = FALSE,
#| eval = TRUE,
#| out.width = "0.7\\textwidth",
#| fig.env = "figure*",
#| fig.cap = "Scenario design matrix for future climate prediction based on SSP
#|   and RCP in ScenarioMIP\\citep{oneill2016scenario}"

knitr::include_graphics("figures/ssp-hires.png")
```

@@

```{r}
#| workflow,
#| echo = FALSE,
#| eval = TRUE,
#| out.width = "0.7\\textwidth",
#| fig.env = "figure*",
#| fig.cap = "The primary process of using epwshiftr to generate EPW files for future weather"

knitr::include_graphics("figures/workflow-hires.png")
```
